---
title: "2023 Apartment Builings Evaluations Analysis in the City of Toronto "
author: 
  - Yuechen Zhang
thanks: "Code and data are available at: LINK."
date: 09-21-2024
date-format: long
abstract: "In this report, the geographic location, temporal information and evaluation of several aspects of the property's condition provided in the data allow us to learn detailed information about the property's assessed condition, which can be used to identify the condition of the flat, assess maintenance and other needs."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

```


# Introduction

The city's condo market also reflects its level of development and internationalization. When evaluating a Toronto condo building, several key factors must be considered to ensure a full understanding of its value and suitability for potential residents or investors and builders.

With the rapid growth of urban populations, the quality of amenities, safety and other aspects of the living environment in apartment buildings has become a key concern.[@zhong2023high] The housing quality and maintenance of flats is a key factor in the safety and well-being of the people living in a community in a city.

A full understanding of the current state of residential buildings is therefore critical for city residents, builders and government housing authorities. The data presented in this report provides a comprehensive assessment of Toronto's condominium residential buildings, reflecting a variety of indicators of the current condition and management of these properties.



# Data {#sec-data}


```{r}
#| echo: false

library(ggplot2)

# Load the data
data <- read.csv("/Users/zhangyuechen/Downloads/1.csv")

ggplot(data, aes(x = LONGITUDE, y = LATITUDE)) +
  geom_point() +
  labs(title = "Scatter Plot of Latitude vs. Longitude", x = "Longitude", y = "Latitude")
```

Specific assessments of different conditions, including geographic information,and so on are included in the dataset.Housing preferences are critical to home-buying choices and are influenced by a variety of factors. The motto of the real estate industry, ‘location, location, location’, is far-reaching, influencing the success of housing projects and generating highly profitable returns.[@hassan2023importance]

As you can see from the chart, most of Toronto's recorded condos are also clustered between largely similar latitudes and longitudes. This means that this location received favour among condos built in those years.



```{r}
#| echo: false
#| warning: false
#| message: false

ggplot(data, aes(x = YEAR.BUILT)) +
  geom_histogram(binwidth = 5, fill = "red", color = "black") +
  labs(title = "Histogram of Year Built", x = "Year Built", y = "Frequency")

```

The year a building was constructed is a key factor in its evaluation. Older buildings constructed many years ago will usually have stronger structures and more living space than newer flats in recent years. However, these buildings also face maintenance issues such as infrastructure that may need to be upgraded.

As you can clearly see from the charts made from the data, the years of construction of the condominiums are concentrated between 1950-1990, which means that the buildings are older as of today. In 2008, Toronto launched a new Renewal Opportunities Handbook, which outlines the basic assessment process and improvement options for aging buildings.[ @mcclelland2011reassessing]. This all-encompassing renewal and maintenance programme has brought new life to the apartment.



```{r}
#| echo: false
#| warning: false
#| message: false
ggplot(data, aes(x = PROPERTY.TYPE)) +
  geom_bar(fill = "yellow") +
  labs(title = "Bar Plot of Property Type", x = "Property Type", y = "Count")
```
Toronto, as Canada's most populous city, is predicted to be home to more than 3.9 million people (Government of Ontario, 2021). As the city continues to become more densely populated, this means that Toronto's housing projects will be multi-unit residential buildings.[@ouyangcomparing] The ownership type of the homes is defined as being Private, so as you can see in the bar chart, Private types make up the vast majority of the Toronto area.

Unlike housing that is privately owned, TCHC is a public agency responsible for providing affordable housing to low and moderate income residents of Toronto. The primary purpose of these flats is to subsidise those who cannot afford market-rate housing and to ensure that all residents have access to safe and stable living conditions.

# Discussion


Condo building appraisal reports are especially important when people are looking for a place to live in Toronto that suits their needs. The year the building was constructed gives an idea of the building's potential maintenance needs and living space. Location determines the lifestyle and amenities offered by the building, while property type determines the living experience and target demographic.

Clearly documented data on attributes of interest will make finding a home more efficient and provide government agencies and builders with reliable data to help them identify suitable properties.



## Weaknesses and next steps

If there are shortcomings that exist, then I think the search could be made more detailed and expand the scope of the survey. For example, there are a lot of new flats built in the last two years that don't seem to be counted in the register. Often these new flats are also the key targets for people to focus on.
The next enhancement could be to add more proximity to the assessment indicators. Although the indicators in the data are already detailed, the data could be updated in real time. This would provide more insight into the current state of urban housing quality.


\newpage


# References


